Constraining Speed of Gravitational Wave and {N}ewton's Constant in Binary Systems

### 2023-03-09 paper.tex
a: f_GW = const
add plot of GW170817
append paper

It is known that if $c\equiv c_0$, $G\equiv G_0$ everywhere, then the amplitude $h$ of GW produced by an inspiring binary satisfies
\begin{equation}
    h\propto\frac{\frac{G_0\mathcal{M}}{c_0^3}[\pi \frac{G_0\mathcal{M}}{c_0^3}F(t)]^{2/3}}{r/c_0}\cos[\int 2\pi F(t)\,\d t],
\end{equation}
where $\mathcal{M}$ is the chirp mass of binary and $F$ is the frequency of GW. Therefore in the region $r\leq R$ mentioned above,
\begin{equation}
    h\propto\frac{\frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}F(t)]^{2/3}}{r/c_\text{s}}\cos[\int 2\pi F(t)\,\d t],
\end{equation}
and then on Earth,
\begin{equation}
    h\propto\sqrt{\frac{c_\text{s}^4/G_\text{s}}{c_0^4/G_0}}\frac{\frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}F(t)]^{2/3}}{d/c_\text{s}}\cos[\int 2\pi F(t)\,\d t],
\end{equation}
where $d$ is the physical distance of binary. Considering the red shift, the amplitude of GW produced by an inspiring binary on Earth satisfies
\begin{equation}
    h\propto\sqrt{\frac{c_\text{s}^4/G_\text{s}}{c_0^4/G_0}}\frac{\frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}F(t)]^{2/3}}{d/c_\text{s}}\cos[\int 2\pi \frac{F(t)}{1+z}\,\d t],
\end{equation}
where $z$ is the red shift of binary. If we define $F_\text{obs}(t)=F(t)/(1+z)$ and $\mathcal{M}_\text{obs}=\mathcal{M}(1+z)$, then
\begin{equation}
    h\propto\sqrt{\frac{c_\text{s}^6/G_\text{s}}{c_0^6/G_0}}\frac{\frac{G_\text{s}\mathcal{M}_\text{obs}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}_\text{obs}}{c_\text{s}^3}F_\text{obs}(t)]^{2/3}}{d_\text{L}/c_0}\cos[\int 2\pi F_\text{obs}(t)\,\d t],
\end{equation}
where $d_\text{L}=d(1+z)$ is the luminosity distance of binary. However, in former researches, $h$ was assumed to satisfy
\begin{equation}
    h\propto\frac{\frac{G_0\mathcal{M}_\text{obs}}{c_0^3}[\pi \frac{G_0\mathcal{M}_\text{obs}}{c_0^3}F_\text{obs}(t)]^{2/3}}{d_\text{L}/c_0}\cos[\int 2\pi F_\text{obs}(t)\,\d t],
\end{equation}
therefore, $d_\text{L,G}$, the result of measuring $d_\text{L}$ by using GW observation data and methods in former researches, will satisfy
\begin{equation}
    \sqrt{\frac{G_\text{s}/c_\text{s}^6}{G_0/c_0^6}}=\frac{d_\text{L,G}}{d_\text{L}},
\end{equation}
where $d_\text{L}$ can also be measured precisely by using EMW observation data, if we assume that the speed of EMW is still $c_0$ everywhere.

@@

\section{Conclusion}
In this paper, we provided a method to constrain speed of GW $c$ and Newton's constant $G$ in binary systems by comparing the results, which are obtained by using GW and EMW observation data and methods in former researches, of measuring the luminosity distances of the binary systems. This method can be practicable when \eqref{lorentz} and \eqref{maxwell} are vaild, together with:
\begin{enumerate}
    \item the speeds of two components of binary are low;
    \item in a spherical region where binary is located at the center, $c$ and $G$ are nearly constants, and the radius of the region is much greater than the distance between two components of binary;
    \item both $c$ and $G$ are only related to $r$, the distance from binary;
    \item $\frac{\d}{\d r}\ln c$, $\frac{\d}{\d r}\ln G$, $\frac{\d^2}{\d r^2}\ln c$, $\frac{\d^2}{\d r^2}\ln G$ are all small.
\end{enumerate}
The strength of constraining $c$ and $G$ by using method provided in this paper is depended on the uncertainties of the results of measuring the luminosity distances, especially that by using GW observation data. Therefore, to strongly constrain $c$ and $G$, results of using GW observation data to measure the luminosity distances in unreached high precision are needed.

>>>>

It is known that if $c\equiv c_0$, $G\equiv G_0$ everywhere, then the amplitude $h$ of GW produced by an inspiring binary satisfies
\begin{equation}
    h\propto\frac{\frac{G_0\mathcal{M}}{c_0^3}[\pi \frac{G_0\mathcal{M}}{c_0^3}F(t)]^{2/3}}{r/c_0}\cos[\int 2\pi F(t)\,\d t],
\end{equation}
where $\mathcal{M}$ is the chirp mass of binary and $F$ is the frequency of GW. Therefore in the region $r\leq R$ mentioned above,
\begin{equation}
    h\propto\frac{\frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}F(t)]^{2/3}}{r/c_\text{s}}\cos[\int 2\pi F(t)\,\d t],
\end{equation}
and then on Earth,
\begin{equation}
    h\propto\sqrt{\frac{c_\text{s}^4/G_\text{s}}{c_0^4/G_0}}\frac{\frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}F(t)]^{2/3}}{d/c_\text{s}}\cos[\int 2\pi F(t)\,\d t],
\end{equation}
where $d$ is the physical distance of binary. Considering the red shift, the amplitude of GW produced by an inspiring binary on Earth satisfies
\begin{equation}
    h\propto\sqrt{\frac{c_\text{s}^4/G_\text{s}}{c_0^4/G_0}}\frac{\frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}F(t)]^{2/3}}{d/c_\text{s}}\cos[\int 2\pi \frac{F(t)}{1+z}\,\d t],
\end{equation}
where $z$ is the red shift of binary. If we define $F_\text{obs}(t)=F(t)/(1+z)$ and $\mathcal{M}_\text{obs}=\mathcal{M}(1+z)$, then
\begin{equation}
    h\propto\sqrt{\frac{c_\text{s}^6/G_\text{s}}{c_0^6/G_0}}\frac{\frac{G_\text{s}\mathcal{M}_\text{obs}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}_\text{obs}}{c_\text{s}^3}F_\text{obs}(t)]^{2/3}}{d_\text{L}/c_0}\cos[\int 2\pi F_\text{obs}(t)\,\d t],\label{new_h}
\end{equation}
where $d_\text{L}=d(1+z)$ is the luminosity distance of binary. However, in former researches, $h$ was assumed to satisfy
\begin{equation}
    h\propto\frac{\frac{G_0\mathcal{M}_\text{obs}}{c_0^3}[\pi \frac{G_0\mathcal{M}_\text{obs}}{c_0^3}F_\text{obs}(t)]^{2/3}}{d_\text{L}/c_0}\cos[\int 2\pi F_\text{obs}(t)\,\d t],\label{old_h}
\end{equation}
therefore, since ${G_\text{s}\mathcal{M}_\text{obs}}/{c_\text{s}^3}$ in \eqref{new_h} and ${G_0\mathcal{M}_\text{obs}}/{c_\text{s}^3}$ in \eqref{old_h} can be individually determined from $F_\text{obs}(t)$, $d_\text{L,G}$, the result of measuring $d_\text{L}$ by using GW observation data and methods in former researches, will satisfy
\begin{equation}
    \sqrt{\frac{G_\text{s}/c_\text{s}^6}{G_0/c_0^6}}=\frac{d_\text{L,G}}{d_\text{L}},
\end{equation}
where $d_\text{L}$ can also be measured precisely by using EMW observation data, if we assume that the speed of EMW is still $c_0$ everywhere.

@@

\section{Conclusion}
In this paper, we provided a method to constrain speed of GW $c$ and Newton's constant $G$ in binary systems by comparing the results, which are obtained by using GW and EMW observation data and methods in former researches, of measuring the luminosity distances of the binary systems. This method can be practicable when \eqref{lorentz} and \eqref{maxwell} are vaild, together with:
\begin{enumerate}
    \item speeds of two components of binary are low;
    \item in a spherical region where binary is located at the center, $c$ and $G$ are nearly constants, and the radius of the region is much greater than the distance between two components of binary;
    \item both $c$ and $G$ are only related to $r$, the distance from binary;
    \item frequency of separate GW remains unchanged.
    \item $\frac{\d}{\d r}\ln c$, $\frac{\d}{\d r}\ln G$, $\frac{\d^2}{\d r^2}\ln c$, $\frac{\d^2}{\d r^2}\ln G$ are all small.
\end{enumerate}
The strength of constraining $c$ and $G$ by using method provided in this paper is depended on the uncertainties of the results of measuring the luminosity distances, especially that by using GW observation data. Therefore, to strongly constrain $c$ and $G$, results of using GW observation data to measure the luminosity distances in unreached high precision are needed.
